%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge Mohammed Mowla} \\ \vspace{1pt}
    \small640-444-0691 $|$ \href{mailto:m.mowla03151@gmail.com}{\underline{m.mowla03151@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/mmowla/}{\underline{linkedin.com/in/mmowla}} $|$
    \href{https://github.com/Collyz}{\underline{github.com/Collyz}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stockton University}{Galloway, NJ}
      {Bachelor of Science in Computer Science, Minor in Mathematics}{Aug. 2020 -- May 2024}
      \resumeSubHeadingListEnd
      \vspace{-3px}\hspace{1em}\small\textbf{GPA:} 3.79 $\vert$  \small\textbf{Honors:} Stockton University Provost's Scholarship (4 Years)


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Federal Aviation Administration}{June 2024 -- Present}
      {Student Intern - A.M.M.S.}{Egg Harbor Township, NJ}
      \resumeItemListStart
        \resumeItem{Developed risk reduction tests for an Air Traffic Technical Operations iOS application, utilizing Appium and Python to ensure robust testing and enhance the app's reliability and performance.}
        \resumeItem{Led a team of interns in the development and implementation of an extensive organizational Wiki site using Confluence and Jira Integration to enhance the efficiency and productivity of the team.}
        \resumeItem{Conducted research on Large Language Models (LLMs) and their potential to accelerate Test and Evaluation (T\&E) processes within the FAA}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
    {Federal Aviation Administration}{June 2023 -- Aug. 2023}
    {Student Intern - A.M.M.S.}{Egg Harbor Township, NJ}
      \resumeItemListStart
        \resumeItem{Led the implementation of Appium automation within a compact test team an  Air Traffic Technical Operations iOS application using Java, and  concurrently documenting manual testing for web and iOS releases.}
        \resumeItem{Assumed co-leadership in a cohort project, providing guidance to team members in understanding and proficiently utilizing virtualized instances of Simulated Driver Radar Recorder (SDRR)}
        \resumeItem{Applied a virtualized Ubuntu shell environment via MobaXTerm to install, use, and gain a comprehensive understanding of the applications of SDRR and its ecosystem.}
    \resumeItemListEnd


    %------ REPLACE WITH RESEARCH IF IT LOOKS BAD : D 
  \resumeSubHeadingListEnd

%-----------RESEARCH-----------
\section*{Research}
    \resumeSubHeadingListStart
      \resumeSubheading
      {Lake Fred Research Project}{Jan. 2023 -- Nov. 2023}
      {Stockton University - Math Research}{Galloway, NJ}
        \resumeItemListStart
        \resumeItem{Gathered geospatial data from Lake Fred at Stockton University and applied the SciPy library, to perform a Convex Hull algorithm for Delaunay Triangulation to extract triangulation information.}
        \resumeItem{Employed Blender's Python API to transform 2K+ points into a triangulation of a 3D model of the lake which allowed for exporting the model into a 3D printable for better visualization and understanding of the lake bed}
        \resumeItem{Developed a website using Three.js, Vite, and Bootstrap to visually depict and interact with the 3D lake model, allowing users to view the surface and wireframe separately.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{DCGAN Animal Image Generation} $|$ \emph{PyTorch, Python, Computer Vision}}{April 2024 -- May 2024}
          \resumeItemListStart
            
            \resumeItem{Conducted preprocessing of images from both the Animal-10N and Kaggle Cats and Dogs datasets, preparing the data for image generation and ensuring optimal input quality for model training and analysis.}
            \resumeItem{Developed and trained several DCGAN models for both cats and hamsters, utilizing Batch Normalization for stability, ReLU for activation functions, and Binary Cross Entropy Loss as the loss function.}
            \resumeItem{Achieved significant results with the Kaggle Cats and Dogs dataset, trained the models for 1K epochs, and processed 12.5K cat images over 140+ minutes, resulted in notable improvements in image generation quality.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Desktop Inventory Application} $|$ \emph{Java, Maven, Git, MySQL, JavaFX MVC, FXML}}{May 2018 -- May 2020}
          \resumeItemListStart
            \resumeItem{Streamlined inventory management for a small South Jersey business by developing a desktop application using JavaFX, FXML, Scene Builder, JavaMail API resulting in a more efficient process.}
            \resumeItem{Implemented CRUD functions for a MySQL database, that validated users to seamlessly manage inventory, enhance security, and reducing manual errors by a significant number}
            \resumeItem{Incorporated sortable tables for all tables through filters such as but not limited to product category, expiration and quantity to improve user experience.}

          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, HTML/CSS, SQL (MySQL), PHP, C\texttt{\#}} \\
     \textbf{Frameworks}{: Node.js, TailWindCSS, Bootstrap, Svelte, WAMP, Apache Tomacat} \\
     \textbf{Developer Tools}{: Visual Studio, IntelliJ, PyCharm, Git, VS Code, Eclipse, Blender, Maple, Angular} \\
     \textbf{Libraries}{: Three.js, p5.js, NumPy, PyTorch, Matplotlib, SciPy, JFreeCharts, JUnit}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}